A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-15 inspiral_svd.tex
added Nick to author list
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@622 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added Toronto to CITA byline
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@623 ccdd05d5-56c1-461a-bf98-85f6876523b4

\author{Kipp Cannon$^1$, Adrian Chapman$^2$, Chad Hanna$^3$, Drew Keppel$^{4,5}$, Antony C. Searle$^2$, Leo Singer$^2$, Alan J. Weinstein$^2$}

\address{$^1$ Canadian Institute for Theoretical Astrophysics, ON, Canada}
\address{$^2$ LIGO Laboratory - California Institute of Technology, Pasadena, CA, USA}
\address{$^3$ Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\address{$^4$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\address{$^5$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}

>>>>

\author{Kipp Cannon$^1$, Adrian Chapman$^2$, Nickolas Fotopoulos$^2$, Chad Hanna$^3$, Drew Keppel$^{4,5}$, Antony C. Searle$^2$, Leo Singer$^2$, Alan J. Weinstein$^2$}

\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON, Canada}
\address{$^2$ LIGO Laboratory - California Institute of Technology, Pasadena, CA, USA}
\address{$^3$ Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\address{$^4$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\address{$^5$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
